\SW Extended! Snappy Titles!

### 2015-05-26 doc/sw-extended.tex
added figure placeholder

@@

>>>>

\subsubsection{Test}

\begin{figure}
\begin{center}
    \includegraphics[scale=]{Figures/}
\end{center}
\caption{This figure will be an ROC curve of the two subtypes in stage2 using
the above way of doing the confusion matrix. Also plotted will be the ROC
curves of the subtypes using just the binary classification. Do we do better by actually specifying? Or are we basically as well
off just taking our binary distribution and dividing up? Failure modes are:
either we don't have enough sims of each subtype to make this worthwhile, or it
doesn't help.}
\label{fig:}
\end{figure}

@@

\subsection{Relaxing Constant Confusion Matrices}
